---
title: "T-Test"
author: "Othmane Jadi"
date: "9/13/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Documents/Junior Year/BIO 490S/Lab 2/")
```

## Importing Dataset

```{r}
election <- read.csv("2008to2016PresElections.csv", header = TRUE, sep =",", dec="."
)
```


## Creating Subsets

```{r}
diff_2012 <- abs(election$Obama.2012-election$Romney.2012)
diff_2016 <- abs(election$Clinton.2016-election$Trump.2016)
```


## Hypothesis

I predict that due to increased political polarization following President Obama's two terms in office, there is a significant increase in the difference between voting outcome for each candidate per district in the 2016 election compared to the 2012 election.


## T-Test

```{r}
t.test(diff_2012,diff_2016,var.equal = TRUE, alternative="less")
```

The t-test shows a significant difference  between the difference of voting outcome for the political candidates in the 2012 election compared to the 2016 election (p = 0.04483).


## Visualization
```{r}
results_names <- c("2012","2016")
boxplot(diff_2012,diff_2016, names=results_names, main="Political Polarization in 2012 vs. 2016", xlab="Difference in Candidate Voting Outcome", horizontal=TRUE)
```



